Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-07-08 patchy-selection-paper.tex
added author summary

% The Spatial Resolution of Convergent Adaptation
% Convergent Evolution in Patchy Landscapes
% Parallel Evolution in Patchy Landscapes

\title{
Convergent Evolution During Local Adaptation to Patchy Landscapes
}

@@

@@

}

>>>>

% short title:  Convergent Evolution on Patchy Landscapes
\title 
{
Convergent Evolution During Local Adaptation to Patchy Landscapes
}

@@

% Keywords
% convergent evolution; parallel evolution; MC1r; local adaptation; landscape genetics; branching processes; reaction-diffusion equations

@@

\textbf{Author Summary:}
Often, a large species range will include patches where the species differs because it has adapted to locally differing conditions.
For instance, rock pocket mice are often found with a coat color that matches the rocks they live in, 
and the difference in coloration is known to be controlled genetically.
Sometimes, similar genetic changes have occurred independently in different patches,
suggesting that there were few accessible ways to evolve the locally adaptive form.
However, the genetic basis could also be shared if
rare migrants may carry the locally beneficial genotypes between nearby patches,
despite being at a disadvantage between the patches.
We use a mathematical model of random migration to determine how quickly adaptation is expected to occur through new mutation or migration from other patches,
and study in more detail what we would expect successful migrations between patches to look like.
The results are useful for determining whether similar adaptations in different locations are likely to have the same genetic basis or not,
and more generally in understanding how species adapt to patchy, heterogeneous landscapes.
}
